---
title: "coc"
author: "Shukra Jaliya"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
coc<-read_csv("coc_data.csv")
```

### Exercise 1

total_population- count of people living in CoC poverty_rate -percent of people living below federal poverty line
Overall Homeless -total homeless population in CoC 
Unsheltered Homeless- count of homeless not sleeping in space designated for or ordinarily used for sleeping 
Sheltered Total Homeless- count of homeless sleeping in shelter or shelter-like facility (publicly or privately funded/owned) 
funding_tot- funding total

```{r code-chunk-label}
#colnames(coc)

```

### Exercise 2

```{r}
coc <- coc %>%
  rename(
    total_homeless_count = `Overall Homeless`,
    unsheltered_homeless_count = `Unsheltered Homeless`,
    sheltered_homeless_count = `Sheltered Total Homeless`,
  )
```

```{r}
coc$homeless_rate <- coc$total_homeless_count / coc$total_population
coc$funding_rate <- coc$funding_tot / coc$total_population
coc$unsheltered_rate <- coc$unsheltered_homeless_count / coc$total_population
coc$sheltered_rate <- coc$sheltered_homeless_count / coc$total_population
```

. HOMELESS RATE

```{r homelessness predicting funding}
#options(scipen = 999)
plot(funding_rate~homeless_rate + total_population, data = coc)
model <- lm(funding_rate~homeless_rate + total_population, data = coc)
summary(model)


```



```{r }

coc$log_funding_rate <- log(coc$funding_rate + 1)
model_log <- lm(log_funding_rate ~ homeless_rate + total_population, data = coc)
summary(model_log)

# Scatter plot for homeless_rate vs log_funding_rate
ggplot(coc, aes(x = homeless_rate, y = log_funding_rate)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Homeless Rate vs Log of Funding Rate", x = "Homeless Rate", y = "Log of Funding Rate")

# Scatter plot for total_population vs log_funding_rate
ggplot(coc, aes(x = total_population, y = log_funding_rate)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "green") +
  labs(title = "Total Population vs Log of Funding Rate", x = "Total Population", y = "Log of Funding Rate")

```





```{r}
coc$log_funding_rate <- log(coc$funding_rate + 1)
model_log <- lm(log_funding_rate ~ homeless_rate + total_population, data = coc)
summary(model_log)
```











```{r}
plot(funding_rate~unsheltered_rate, data = coc)
model1 <- lm(funding_rate~unsheltered_rate + total_population, data = coc)
summary(model1)
```

```{r}
plot(funding_rate~sheltered_rate, data = coc)
model2 <- lm(funding_rate~sheltered_rate + total_population,, data = coc)
summary(model2)
```


```{r}
coc$log_density <- log(coc$pop_density + 1)
model6<-lm(funding_rate ~ homeless_rate + total_population + log_density, data = coc)
summary(model6)
```

...
